
\subsection{Ethics}  
\noindent According to the ACM Code of Ethics, term 1.6 “ensuring the accuracy of data, understanding the provenance of the data…The retention and disposal periods for that information should be clearly defined, enforced, and communicated to data subjects...” \cite{acm-ethics}, computing professionals should always take special care for privacy when merging data collections. For our project, to train our intelligent system and make it to recognize the characteristics of clothing, we must use a huge data set. The data set we want to use in our project collected by MMLAB (The Chinese University of Hong Kong), which is available for non-commercial research purposes and whose images are obtained from the Internet. Therefore, this public data set can be obtained for educational and research purposes and it is reliable and accurate to use.  

\noindent Secondly, by the IEEE Code of Ethics, Section I Policy 5, “ to seek, accept, and offer honest
criticism of technical work, to acknowledge and correct errors, to be honest and realistic in stating claims or estimates based on available data, and to credit properly the
contributions of others.”\cite{ieee-ethics} Our group team welcome all the different opinion and criticism from all kind of groups such as sponsors, teaching assistance and classmates.  

\noindent Moreover, if our group can successfully build this intelligent system, we should pay more attention to copyright issue. From the ACM Code of Ethics, term 1.5,“Computing professionals should therefore credit the creators of ideas, inventions, work…respect copyrights, patents… and other methods of protecting authors' works.”\cite{acm-ethics} To protect the intelligent property of this project, we will save our work carefully and turn to legal protection if necessary.  

\subsection{Safety} 
\noindent The IEEE Code of Ethics, Section I Policy 1 “To hold paramount the safety, health, and welfare of the public... “ is important when considering the use of some electrical devices. For example, for our battery use, which is mounted on NodeMCU, operates at about 3.3V and it is generally safe to use in our daily life. Moreover, the Wifi-enabled part of NodeMCU will not interfere with the operation of other wireless devices nearby.  



